Spike spectra for recurrences

### 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
Merged and minor typos, and rebuttal

Applied to the $\ŧau$-RR this novel spectrum directly reveals the peridocities of the underlying system, also in cases where there is no direct analogue of the power spectrum.
This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, the spikes encode the systems periods, and the inter-spike spectrum can reliably reveal the system's dominant frequencies, 
which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
in the $\tau$-RR are not sensitive to noise, the corresponding inter-spike spectrum also yields robust results in the presence of noise.

>>>>

Applied to the $\tau$-RR this novel spectrum directly reveals the peridocities of the underlying system, also in cases where there is no direct analogue of the power spectrum.
This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, the spikes encode the systems periods, and the inter-spike spectrum can reliably reveal the system's dominant frequencies, 
which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
in the $\tau$-RR are not sensitive to noise, the corresponding inter-spike spectrum also yields robust results in the presence of noise.
